{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-10 Paper/main.tex
Meeting State 10.02.2022

	\title{{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\thispagestyle{empty}
	\vspace{1.5 cm}
	\begin{center}
		University of Bonn \\
		Research Module in Econometrics and Statistics \\
		Winter Semester 2021/2022
	\end{center}
\end{titlepage}
	\newpage

	\tableofcontents

@@

	\section{Introduction}

	Functional Data Analysis (FDA), which has its roots in the work of Ulf Grenander and Kari Karhunen, is gaining more attention as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, FDA has advantages in that it allows extracting information given by properties such as the smoothness of the underlying process or its derivatives (cf. \cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves or functions.	 
	Therefore, data sets in FDA can include both realizations of scalar random variables and realizations of random functions. Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to Appendix \ref{NIR}.}

	This paper introduces Functional Linear Regression in a scalar-on-function setting. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional. 
	We then introduce two distinct ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression. Both of these methods are dependent on a parameter choice called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\

	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures, and address the theoretical importance of the truncation parameter. Section \ref{Simulation} contains a description of our Monte-Carlo Simulation, which aims to provide information on how to choose an appropriate functional basis and truncation parameter for the aforementioned methods. The application in Section \ref{Application} then uses the insights from theory and simulation to choose an appropriate basis for the estimation of octane numbers of gasoline samples based on Near-Infrared absorption curves. In Section \ref{Outlook}, we give an outlook on possible extensions for this paper and describe the limitations of our approach.

	\section{Theory}\label{Theory}
	To allow for scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space. One integral concept that must be defined is random functions as a special case of random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space. 
	The typical case for a random variable realizing in $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition for the concept of a random function, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more in-depth considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015} and chapters 4.4 and 4.6 from \cite{kokoszka_introduction_2017}.

	\subsection{Inner Products and Hilbert Spaces}
	The first concept we will introduce is the concept of Hilbert spaces. To do so, we start from inner product spaces but restrict our analysis to vector spaces over $\mathbb{R}$ for the sake of clarity. Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.  Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space, and the inner product defines a norm and an associated distance on the vector space.
	\begin{equation}
		\lvert \lvert v \rvert \rvert = {\langle v, v \rangle}^{\frac{1}{2}} \quad \text{and} \quad 
		d(v_1, v_2) = {\langle v_2 - v_1, v_2 - v_1 \rangle}^{\frac{1}{2}}
	\end{equation}

@@

	As in the case of a Banach space, each element of a Hilbert space can be expressed in terms of a corresponding basis. This can be done using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t. a basis $S = \{s_n\}$ as follows.
	\begin{equation}
		x = \sum_{j = 1}^{\infty}{\langle x, s_j \rangle}s_j
	\end{equation}

	Differing from the case of Banach spaces, these representations can be limits of series. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements in a Hilbert space is to use a truncated series.
	\begin{equation}
		x \approx \sum_{j = 1}^{K}{\langle x, s_j \rangle}s_j
	\end{equation}

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$. Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. The inner product of $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
	\begin{equation}\label{inner_prod}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
	\end{equation}

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations, but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	A random function on $\mathbb{L}^2[0,1]$ can then be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.

	\subsection{Functional Data Sets}
	If we take a random function $X(\omega)$ as defined in the previous section, then realizations $x(t)$ of $X(\omega)(t)$ are called sample curves of the random function. The presence of functional observations in a data set defines functional data sets. However,  realizations of random functions are not typically observed in their functional form. Instead, each curve is observed at a discrete and typically large set of measurements points. Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points $t_{i,j}$. These measurement points can be different for each sample curve. In this paper, we only consider the case where curves share their measuring points.
	To use the unique capabilities of functional data analysis with functional data obtained in this form, it is necessary to restore its functional structure. Therefore, methods such as basis representations will be introduced in the following parts of the Theory Section.\\
	As in the finite-dimensional setting, the concept of identically distributed and independent data is important for many aspects of functional data analysis. One example of i.i.d. curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d. random process itself. More information about this example can be found in Appendix \ref{NIR}.

	\subsection{Representing a Function in terms of a Basis}\label{bases}
	As previously described, a basis of a Hilbert space can be used to express its elements using the corresponding Fourier expansion. Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express or approximate a realization $x(t)$ of $X(\omega)$. The following equation shows how a basis can be used to express a function as a weighted sum of its elements.
	\begin{equation}
		x(t) = \sum_{j \in \mathcal{I}} a_j \phi_j(t) 
	\end{equation}

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing a number of basis functions from these bases are found in Section \ref{Basis_Plots} of the Appendix.
	\vspace{-0.2cm}

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use monomials of increasing degree as a basis. For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$. Nevertheless, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis for approximation. \\
	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero, as shown above. Instead, one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}

	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$. However, a different choice of $\alpha$ could lead to improvements in the performance of the Monomial basis.
	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. These problems will be addressed in more detail in later parts of this paper. The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf. \cite{ramsay_functional_2005}).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In the same way the Monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions. Equation \ref{Fourier_Series} shows an example for a function with a period of 1.
	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_i \cos(2\pi i x - \phi_i) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

	Typically, the series is represented in the so-called amplitude-phase form. This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter. Therefore, rewriting the series in the sine-cosine form, as shown above, is necessary.
	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.

	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	To stay true to the original amplitude-phase form, it is reasonable to restrict the number of Fourier basis functions to odd-numbered values. The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process. The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions. (cf. \cite{ramsay_functional_2005})
	\vspace{-0.2cm}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree. If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_l$. A typical case that is often used in practice is an equidistant grid of knots. In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure, allowing for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

	B-splines are a specific system of spline functions developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure. Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows. 
	\begin{equation}
		\begin{split}
			\phi_{l,0}^{BS}(x) = &
			\begin{cases}
				1 & \text{if} \quad x \in \left[\tau_l, \tau_{l+1}\right)\\
				0 & \text{otherwise}
			\end{cases}\\ \\
			\phi_{l,m}^{BS}(x) = &\frac{x - \tau_l}{\tau_{l+m} - \tau_l} \phi_{l,m-1}^{BS}(x) + \frac{\tau_{l+m+1} - x}{\tau_{l+m+1} - \tau_{l+1}} \phi_{l+1,m-1}^{BS}(x)
		\end{split}
	\end{equation}

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$, an additional $m$ times. This padding of the knot vector then allows calculating every object that is needed for the definition of the basis over the original set of knots.\\	
	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.

	\subsection{Approximation and Smoothing via Basis Truncation}
	Realized curves from a data set can be expressed in terms of a chosen functional basis. For this expansion, it is possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases, this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting. To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves. On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information. This is a typical occurrence of the Bias-Variance tradeoff.\\

	A different approach that is atypical in practice is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects. Here, the parameter of choice is not a weighting term for the penalty but the number of basis functions. Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper. A truncated basis expansion as described above is given in Equation \ref{basis_exp}.
	\begin{equation}\label{basis_exp}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations. $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set, which is used in the later parts of this paper and exemplifies the tradeoffs at the core of the truncation parameter choice.

>>>>

	\title{{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}}
	\author{Jonghun Baek, Jakob R. Juergens, Jonathan Willnow}
	\date{11.02.2022}
	\maketitle
	\thispagestyle{empty}
	\vspace{1.5 cm}
	\begin{center}
		University of Bonn \\
		\vspace{0.2cm}
		Research Module in Econometrics and Statistics \\
		Supervised by: Prof. Dr. Dominik Liebl and Dr. Christopher Walsh \\
		\vspace{0.2cm}
		Winter Semester 2021/2022
	\end{center}
\end{titlepage}
	\newpage

	\thispagestyle{empty}
	\tableofcontents

@@

	\pagenumbering{arabic}
	\section{Introduction}

	Functional Data Analysis (FDA) has its roots in the work of Ulf Grenander and Kari Karhunen and is gaining traction as researchers from different fields collect data that is functional in nature. Although classical statistical methods can often process this data, FDA has advantages allowing it to extract information given by properties such as the smoothness of the underlying process or its derivatives (cf. \cite{levitin_introduction_2007}).	As \cite{kokoszka_introduction_2017} describe, using methods from FDA should be considered when one variable of a given data set can be seen as smooth curves.	 
	Examples of such curves are the absorption curves of electromagnetic radiation in the Near-infrared (NIR) spectrum by chemical samples.\footnote{For more details on Near-Infrared-Spectroscopy, refer to Appendix \ref{NIR}.}

	This paper introduces Functional Linear Regression in a scalar-on-function setting. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional. 
	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression. Both methods depend on a parameter called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\

	In Section \ref{Theory}, we introduce the necessary theoretical concepts, describe the estimation procedures, and address the theoretical importance of the truncation parameter. Section \ref{Simulation} contains a description of our Monte-Carlo Simulation, which aims to provide information on how to choose an appropriate functional basis and truncation parameter for the aforementioned methods. The application in Section \ref{Application} uses the insights from theory and simulation to choose an appropriate basis for the estimation of octane numbers of gasoline samples based on Near-Infrared absorption curves. In Section \ref{Outlook}, we describe the limitations of our approach and give an outlook on possible extensions for this paper.

	\section{Theory}\label{Theory}
	To introduce scalar-on-function regression, it is necessary to extend some concepts from multivariate regression to the realm of infinite-dimensional objects, as the statistics derived from infinite-dimensional random functions cannot be defined on a finite-dimensional space. One integral concept that must be defined are random functions as a special case of random variables. Paraphrasing a definition by \cite{bauer_wahrscheinlichkeitstheorie_2020}, a random variable $X:\Omega \rightarrow \Omega'$ is an $\mathcal{A} \text{-} \mathcal{A'} \text{-measurable}$ function, where $(\Omega, \mathcal{A}, P)$ is a probability space and $(\Omega', \mathcal{A'})$ is a measure space. 
	The typical case for a random variable realizing in $\mathbb{R}$ is $(\Omega', \mathcal{A'}) = (\mathbb{R}, \mathcal{B})$, where $\mathcal{B}$ is the canonical $\sigma$-algebra on the real numbers. As a first intuition, it is possible to imagine a similar concept where a random variable does not realize as an element of the real numbers but as a function in a function space. A formalization of this idea makes some more in-depth considerations necessary. The following theoretical introduction closely follows chapters 2.3 and 2.4 from \cite{hsing_theoretical_2015} and chapters 4.4 and 4.6 from \cite{kokoszka_introduction_2017}.

	\subsection{Inner Products and Hilbert Spaces}
	The first concept we will introduce is the concept of Hilbert spaces. We start from inner product spaces but restrict our analysis to vector spaces over $\mathbb{R}$ for clarity. Let $\mathbb{V}$ be a vector space over $\mathbb{R}$.  Then, a function $\langle \cdot, \cdot \rangle : \mathbb{V} \times  \mathbb{V} \rightarrow \mathbb{R}$ is called an inner product, if $\forall v, v_1, v_2 \in \mathbb{V}$ and $a_1, a_2 \in \mathbb{R}$ the following properties hold.

@@

	A vector space with an associated inner product is called an inner product space. The inner product defines a norm and an associated distance on the vector space.
	\begin{equation}
		\lvert \lvert v \rvert \rvert = {\langle v, v \rangle}^{\frac{1}{2}} \quad \text{and} \quad 
		d(v_1, v_2) = {\langle v_2 - v_1, v_2 - v_1 \rangle}^{\frac{1}{2}}
	\end{equation}

@@

	Each element of a Hilbert space can be expressed in terms of a corresponding basis. Using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t. a basis $S = \{s_n\}$ leads to the following representation.
	\begin{equation}
		x = \sum_{j = 1}^{\infty}{\langle x, s_j \rangle}s_j
	\end{equation}

	Differing from the finite-dimensional case, these representations can be limits of series. As using an infinite number of basis functions is infeasible in applied contexts, an intuitive way to approximate elements in a Hilbert space is to use a truncated series.
	\begin{equation}
		x \approx \sum_{j = 1}^{K}{\langle x, s_j \rangle}s_j
	\end{equation}

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}\label{L_2}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$, but analogous constructions can be made for different domains. Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. The inner product on $\mathbb{L}^2[0,1]$ is defined by Equation \ref{inner_prod}.
	\begin{equation}\label{inner_prod}
		\langle f_1, f_2 \rangle = \int_{0}^{1} f_1 f_2 \mathrm{d}\mu.
	\end{equation}

	A random function on $\mathbb{L}^2[0,1]$ can now be defined formally as a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$.

	\subsection{Functional Data Sets}
	If we take a random function $X(\omega)$ as defined in the previous section, then its realizations $x(t)$ are called sample curves of the random function. This presence of functional observations $x_i(t)$ in a data set defines functional data sets. However,  realizations of random functions are not typically observed in their functional form. Instead, each curve is observed at a set of discrete measurement points. Consider the case of a data set containing observations $x_i(t)$ of a random function $X(\omega)$
	\begin{equation}
		x_{i}(t_{i,j}) \in \mathbb{R}, \quad i = 1,\: \dots\: ,N, \; j = 1, \: \dots \:, J_i, \; t_{i,j} \in [T_1, T_2]
	\end{equation}

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at measurement points $t_{i,j}$. These measurement points can be different for each sample curve. In this paper, we only consider the case where curves share their measuring points.
	To use the unique capabilities of functional data analysis with functional data obtained in this form, it is necessary to restore its functional structure. Therefore, we introduce methods such as basis representations in the following parts of the Theory Section.\\
	As in the finite-dimensional setting, the concept of independent and identically distributed (i.i.d.) data is important for many aspects of functional data analysis. One example of i.i.d. curves could be Near-Infrared absorption spectra of gasoline samples where each sample is produced by the same production process and can therefore be interpreted as a realization of and i.i.d. random process itself. More information about this example can be found in Appendix \ref{NIR}.

	\subsection{Representing a Function in terms of a Basis}\label{bases}
	As previously described, a basis of a Hilbert space can be used to express its elements using a Fourier expansion. Let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis used to express a realization $x(t)$ of $X(\omega)$. The following equation shows how to use a basis to express a function as a weighted sum of its elements.
	\begin{equation}
		x(t) = \sum_{j \in \mathcal{I}} a_j \phi_j(t) 
	\end{equation}

	One very important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$. For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing these bases are found in Section \ref{Basis_Plots} of the Appendix.
	\vspace{-0.2cm}

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use the monomials as a basis. For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$. However, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole.
	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero, as shown above. Instead, one can introduce a shift parameter $\alpha$. This leads to the following formalization of the Monomial basis.
	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i \quad i \in \mathbb{N}
	\end{equation}

	Due to the implementation of our simulation, we limit our paper to the case of $\alpha = 0$. A different choice of $\alpha$ could lead to performance improvements.
	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. The effects of this problem will be addressed in more detail in later parts of this paper. The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf. \cite{ramsay_functional_2005}).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In the same way the Monomial basis is connected to the Taylor series, the Fourier basis corresponds to the Fourier series, which can be used to decompose a periodic function into trigonometric functions. Equation \ref{Fourier_Series} shows an example for a function $s(x)$ with a period of $T = 1$.
	\begin{equation}\label{Fourier_Series}
		s(x) = \frac{A_0}{2} + \sum_{i = 1}^{\infty} A_i \cos(2\pi i x - \phi_i) = \frac{a_0}{2} + \sum_{i = 1}^{\infty}\left[a_i \cos(2\pi i x) + b_i \sin(2\pi i x)\right]
	\end{equation}

	Typically, the series is represented in the so-called amplitude-phase form. This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter. Rewriting the series in its sine-cosine form, as shown above, is necessary.
	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.

	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	To stay true to the original amplitude-phase form, it is reasonable to restrict the number of Fourier basis functions to odd-numbered values. The Fourier basis' elements are cyclical which is useful to expand functions that represent a periodic or seasonal underlying process. Due to the nature of the trigonometric functions, it is especially suitable to expand functions with a similar curvature across their domain, resulting in uniformly smooth expansions. (cf. \cite{ramsay_functional_2005})
	\vspace{-0.2cm}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_B]$ into $B$ subintervals of non-negative length bounded by a non-decreasing sequence of points $(\tau_b)_{b = 0, \: \dots \:, B}$ called knots. On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree. If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_b$. A typical case that is often used in practice is an equidistant grid of knots. In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure, allowing for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

	B-splines are a specific system of spline functions developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure. Let $\phi_{b,m}^{BS}(x)$ for $b \in \{1, \: \dots \:, B + m - 2\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_B]$ and knots $\{\tau_b \: \vert \: b = 0, \:\dots \:, B\}$, then it is defined by the Cox-de Boor recursion formula as follows. 
	\begin{equation}
		\begin{split}
			\phi_{b,0}^{BS}(x) = &
			\begin{cases}
				1 & \text{if} \quad x \in \left[\tau_b, \tau_{b+1}\right)\\
				0 & \text{otherwise}
			\end{cases}\\ \\
			\phi_{b,m}^{BS}(x) = &\frac{x - \tau_b}{\tau_{b+m} - \tau_b} \phi_{b,m-1}^{BS}(x) + \frac{\tau_{b+m+1} - x}{\tau_{b+m+1} - \tau_{b+1}} \phi_{b+1,m-1}^{BS}(x)
		\end{split}
	\end{equation}

	As this equation references knots that are not defined by the original vector of knots, implementations typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_B$, an additional $m$ times. This padding of the knot vector allows calculating every object that is needed for the definition of the basis over the original set of knots.\\	
	This does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. However, to focus on specific approximation errors in the later parts of this paper, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	As the B-spline basis does not have infinitely many elements, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$. For the sake of keeping the notation concise, we will still keep this notation. By convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.

	\subsection{Approximation and Smoothing via Basis Truncation}
	Realized curves from a data set can be expressed in terms of a chosen functional basis. For this expansion, it is possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases, this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting. To combat this problem, smoothing methods such as acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves. On the other hand, important information on the curves could be missed by oversmoothing the data, giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information. This is a typical occurrence of the Bias-Variance tradeoff.\\

	A typical setup is described by \cite{Goldsmith_2011} in which an explicit smoothness term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high. To provide intuition for this approach, let 
	\begin{equation}
		PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	\end{equation}

	A different approach is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects. Here, the parameter of choice is not a weighting term for the penalty but the number of basis functions. Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper. A truncated basis expansion as described above is given in Equation \ref{basis_exp}.
	\begin{equation}\label{basis_exp}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} a_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} a_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} a_j(\omega_0) \phi_j(t)
	\end{equation}

	Here, $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations. $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation (CV). Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one NIR absorption curve from the gasoline data set, which exemplifies the tradeoffs at the core of the truncation parameter choice.
